Time for a rethink: disparity-through-time

### 2017-12-04 manuscript/tables/datasets.tex
Markdown to easily build the tables (example done with table 1)

% Dataset descriptions table

\begin{tabular}[t]{l p{3cm} l l l l}

\hline
\textbf{Dataset} & \textbf{Group} & \textbf{$N_{taxa}$} & \textbf{$N_{characters}$} & \textbf{Age range} & \textbf{Reference} \\
\hline
Beck2014 & Eutherian mammals & 102 & 410 & 170 Ma - present & X \\
%-----------------------------------------------------------
Bapst2016 & theropods & 102 & 410 & 170 Ma - present & X \\
%-------------------------------------------------------
Brusatte2014 & theropods & 102 & 410 & 170 Ma - present & X \\
%-------------------------------------------------------
Heath2016 & bears & 102 & 410 & 170 Ma - present & X \\
%-------------------------------------------------------
Wright2017 & crinoids & 102 & 410 & 170 Ma - present & X \\
%-------------------------------------------------------
\hline
\end{tabular}

>>>>

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Dec  4 13:30:53 2017
\begin{table}[ht]
\centering
\begin{tabular}{rlrrlll}
  \hline
 & Group & n taxa & m characters & Age range & Reference & Notes \\ 
  \hline
Beck2014 & Eutherian mammals & 106 & 421 & 171.786 - 0 &  &  \\ 
  Brusatte2014 & theropods & 152 & 853 & 102.535 - 0 &  & 2 + 9 taxa removed \\ 
  Bapst2016 & theropods &  89 & 374 & 141.216 - 0 &  & 12 + 19 taxa removed. Tree was randomly selected from all time-scaled trees \\ 
  Heath2016 & bears &  18 &  62 & 33.241 - 0 &  & 12 + 0 taxa removed \\ 
  Wright2017 & crinoids &  42 &  87 & 485.4 - 372.2 &  & Maximum clade credibility tree, time-scaled by dividing branches by 0.03517385 and setting root time to 485.4 \\ 
   \hline
\end{tabular}
\caption{Details of the datasets used in this study.} 
\end{table}
